Diverse snow algae blooms in the alpine and subalpine zones of British Columbia

### 2020-01-08 manuscript/manuscript.Rmd
fixed refs

<!-- why microscopy not reliable -->
Much of the previous work on snow algae relied on cell morphology for identification, but microscopic identification of snow algae can be unreliable. The same species can look completely different with different environmental conditions of life stages. For example, cultured *Chloromonas krienitzii* cells are small green biflagellates, but field samples cells of this species are larger orange spheres with thick walls and short spines [@matsuzaki_revisiting_2015]. In the freshwater green algae *Haematococcus pluvialis* red pigment is produced in response to stress conditions [@shah_astaxanthin_2016], and @muller_persistant_2001 hypothesized that red Arctic snowfields develops from green snow, but thus far genetic studies have failed to support this hypothesis [@terashima_microbial_2017;@lutz_integrated_2015]. Different species of snow algae can look nearly identical: recent phylogenetic work found that four distinct field samples dominated by similar-looking cells previously referred to as *Chloromonas cf. nivalis* are actually genetically distinct clades [@matsuzaki_taxonomic_2019].

@@

# Methods {-}

>>>>

<!-- why microscopy not reliable -->
Much of the previous work on snow algae relied on cell morphology for identification, but microscopic identification of snow algae can be unreliable. The same species can look completely different with different environmental conditions of life stages. For example, cultured *Chloromonas krienitzii* cells are small green biflagellates, but field samples cells of this species are larger orange spheres with thick walls and short spines [@matsuzaki_revisiting_2015]. In the freshwater green algae *Haematococcus pluvialis* red pigment is produced in response to stress conditions [@shah_astaxanthin-producing_2016], and @muller_persistent_2001 hypothesized that red Arctic snowfields develops from green snow, but thus far genetic studies have failed to support this hypothesis [@terashima_microbial_2017;@lutz_integrated_2015]. Different species of snow algae can look nearly identical: recent phylogenetic work found that four distinct field samples dominated by similar-looking cells previously referred to as *Chloromonas cf. nivalis* are actually genetically distinct clades [@matsuzaki_taxonomic_2019].

@@

# Materials and Methods {-}
